% !TEX root = ../main.tex

\chapter{Acknowledgements}% (fold)
\label{chp:acknowledgements}

First of all I want to thank everyone at Algolia for helping me in several ways, be it by reviewing, reading or just general knowledge they gave me. In particular I'd like to thank Vincent Voyer for being a great mentor that absolutely cares about what I make, but also for being someone who might actually get me into sporting regularly.

I'd like to thank as well Kevin Granger, Sylvain Utard and everyone else that helped with the Yarn project, which really kick-started my internship and research. I also want to thank everyone else in the JavaScript team, Alex Stanislawski, Marie-Laure Thuret, Maxime Janton --- and also Raymond Rutjes, who regularly actually writes php --- for all tips and tricks that helped me during my internship and my project. I also specifically want to thank Lucas Bonomi, Sylvain Utard and Marion Aguirre for helping me with the opportunity to get this internship.

I also want to thank everyone that helped me when making Yarn, working at Facebook: Daniel Lo Nigro, Christoph Pojer, Konstantin Raev and Sebastian McKenzie, as well as other people contributing, among which Espen Henriksen, Ken Sin, Maël Nilson and notably James Kyle, as well as a lot more incredible people.

I also want to thank Eva Naudts, Joris Maervoet and everyone else reading or reviewing, for finding all my mistakes.

I would like to give a special mention to my grandfather, Georges Viaene, who passed away during my time in France. Coming back to Belgium, and seeing him light up when I explained what I was doing at this internship was a very special moment for me. 
